Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not violated for any $k>\overline{k}$. 
Then, it is sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.

Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
The check that these assumptions are sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.

>>>>

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k>\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 5):

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming a plan't
precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.
